---
title: "individual1"
author: "Kordell Schrock"
date: "9/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(devtools)
library(hash)
library(hashmap)
library(data.table)

choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```
1. How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.
```{r}
ggplot(choco, aes(x=Rating)) + geom_histogram(binwidth=.25,color = "black", fill = "gray")+ labs(title="Histogram of Ratings of Choco Bins=.25") + geom_vline(aes(xintercept=median(Rating)), color="blue", linetype="dashed") +scale_x_continuous(breaks = scales::pretty_breaks(n = 12)) 

ggplot(choco, aes(x="Rating", y=Rating))+geom_boxplot(outlier.colour="red", outlier.shape=8, outlier.size=4, color='blue') + labs(title="Ratings")


```

  
  
    1.Answer: We can see that the data there are 4 outliers in the data from the Boxplot. When I changed the binwidth to .25 we can see that the data is a little bit skewed in the Histogram. The Median of the Data is ~3.25.
    
2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.   
```{r}
sortedData <- choco[order(choco$Date),]
ratingsByYear <- aggregate(Rating ~ Date, data = sortedData, FUN = function(x){NROW(x)})

ggplot(data=ratingsByYear, aes(x=Date, y=Rating)) +
  geom_bar(stat="identity", fill="steelblue",)+
  geom_text(aes(label=Rating), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + labs(title="Number of Ratings by Year")


```

    2.Answer: We can see that the Number of Ratings Report per year has been steadly increasing to 2015. The major decrease in Rating Reports were for years 2017 and 2020.

3. Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain.
```{r}
ratingsByCacaoPercent <- aggregate(Rating ~ Cocoa_Percent, data = choco, mean)

ggplot(ratingsByCacaoPercent, aes(x=Cocoa_Percent)) + geom_histogram(bins = 12, color = "black", fill = "gray")+ geom_vline(aes(xintercept=median(Cocoa_Percent)), color="blue", linetype="dashed") +scale_x_continuous(breaks = scales::pretty_breaks(n = 12)) 

ggplot(ratingsByCacaoPercent, aes(x=Cocoa_Percent, y=Rating))+geom_boxplot(outlier.colour="red", outlier.shape=8, outlier.size=4, color='blue') + labs(title="Ratings")

ggplot(ratingsByCacaoPercent, aes(x=Cocoa_Percent, y=Rating)) +
  geom_point() + 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  theme_classic()
correlation <- cor(ratingsByCacaoPercent$Cocoa_Percent, ratingsByCacaoPercent$Rating)
ratingsByCacaoPercent
correlation
```
    
    3.Answer: I would say the Cocoa Percent does not matter that much because if you look at the histogram it is evenly distributed. In addition, I added a scatter plot with a line of best fit. Since the Correlatin of the Variables Cocoa Percent and Ratings is -.17, this means that they are not correlated since the number is close to 0.

4. How do different characteristics of the chocolate compare? To elaborate, which characteristics tend to be more favorable and which ones are not? Create both numerical and graphical summaries, and explain.
```{r}
ratingsByCharacteristic1 <-  data.frame(aggregate(Rating ~ Characteristics1, data = choco, mean))
ratingsByCharacteristic2 <-  data.frame(aggregate(Rating ~ Characteristics2, data = choco, mean))
ratingsByCharacteristic3 <-  data.frame(aggregate(Rating ~ Characteristics3, data = choco, mean))
ratingsByCharacteristic4 <-  data.frame(aggregate(Rating ~ Characteristics4, data = choco, mean))

names(ratingsByCharacteristic1)[1] <- "characteristics"
names(ratingsByCharacteristic2)[1] <- "characteristics"
names(ratingsByCharacteristic3)[1] <- "characteristics"
names(ratingsByCharacteristic4)[1] <- "characteristics"


DF <- do.call(rbind, list(ratingsByCharacteristic1,ratingsByCharacteristic2,ratingsByCharacteristic3,ratingsByCharacteristic4))
DT <- data.table(DF)
print(DT)

averages <- aggregate( Rating ~ characteristics, DT, mean )
averagesSorted <- averages[order(-averages$Rating), ]
top30Characteristics <- averagesSorted[1:30,]
print(top30Characteristics)


top5Characteristics <- averagesSorted[1:5,]

ggplot(data=top5Characteristics, aes(x=characteristics, y=Rating)) +
  geom_bar(stat="identity", fill="steelblue",)+
  geom_text(aes(label=Rating), vjust=1.6, color="white", size=3.5)+ labs(title="Top 5 Rated Characteristics")

averagesSortedWorst <- averages[order(averages$Rating), ]
worst30Characteristics <- averagesSortedWorst[1:30,]
print(worst30Characteristics)
worst5Characteristics <- averagesSortedWorst[1:5,]

ggplot(data=worst5Characteristics, aes(x=characteristics, y=Rating)) +
  geom_bar(stat="identity", fill="steelblue",)+
  geom_text(aes(label=Rating), vjust=1.6, color="white", size=3.5)+ labs(title="Worst 5 Rated Characteristics")

```
    
    4.Answer: Looking at the data there are ~30 Characteristics that are rated 4. The way I found this was combining all 4 Characteristics into 1 column and combine their scores and finding the mean for each Characteristic. Looking through the data we can see that people have different Characteristics they look for in chocolate. Some Characteristics are better than others. 

5. Brainstorm two analyses you would like to perform with your teammate. Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.
```{r}
# Find the top 5 rated companies 
companies <-  data.frame(aggregate(Rating ~ Company, data = choco, mean))
companiesSorted <- companies[order(-companies$Rating), ]
top5Companies <- companiesSorted[1:5,]
# Find the worst 5 rated companies 
companiesSortedWorse <- companies[order(companies$Rating), ]
worst5Companies <- companiesSortedWorse[1:5,]
ggplot(data=top5Companies, aes(x=Company, y=Rating)) +
  geom_bar(stat="identity", fill="steelblue",)+
  geom_text(aes(label=Rating), vjust=1.6, color="white", size=3.5)+ labs(title="Top 5 Rated Companies To Buy From")

ggplot(data=worst5Companies, aes(x=Company, y=Rating)) +
  geom_bar(stat="identity", fill="steelblue",)+
  geom_text(aes(label=Rating), vjust=1.6, color="white", size=3.5)+ labs(title="Worst 5 Rated Companies Not To Buy From")


```
    
    5.Answer: Here I wanted to look at the top 5 rated companies. Also, the top worst companies and list then. This would be helpful to show people which companies are best to buy from for chocolate.


